### 2015-11-20 section/3_redundancy.tex
emphasize sampling does not hurt quality

Note that, \Tool leverages sampling to gain performance with \textbf{no}
sacrifice to diagnosis latency or quality, which is
\textbf{different} from traditional sampling techniques
for diagnosing correctness failures \cite{liblit03,liblit05}, where
many more failure runs and hence longer diagnosis latency
are needed to compensate for the performance gain.
Performance bugs have a unique repetitive nature:
a loop can cause a severe performance problem only when it 
contains many redundant iterations/instances.
Therefore, we can still recognize redundant behavior in just
\textbf{one} failure run, 
as long as the sampling is not insanely sparse
(Section \ref{sec:experiment}). 
%Another observation, which can also be demonstrated by examples shown in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
%is that two consecutive loop instances are good targets to compare.

>>>>

Note that, \Tool leverages sampling to gain performance with almost \textbf{no}
sacrifice to diagnosis latency or quality, which is
\textbf{different} from traditional sampling techniques
for diagnosing correctness failures \cite{liblit03,liblit05}, where
many more failure runs and hence longer diagnosis latency
are needed to compensate for the performance gain.
The reason is that performance bugs have a unique repetitive nature:
a loop can cause a severe performance problem only when it 
contains many redundant iterations/instances.
Therefore, we can still recognize redundant behavior in just
\textbf{one} failure run, 
as long as the sampling is not insanely sparse
(Section \ref{sec:experiment}). 
%Another observation, which can also be demonstrated by examples shown in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
%is that two consecutive loop instances are good targets to compare.

### 2015-11-20 section/5_exper.tex
emphasize sampling does not hurt quality

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcc}
    \toprule
                            	&  {\bf Reported}             &{\bf Fix }                     \\
   {\bf BugID}                  &  {\bf Root Cause}           &{\bf Suggestion}             \\
   \midrule
   Mozilla347306                & \Yes                        & \Yes                                          \\
   Mozilla416628                & \Yes                        & \Yes                                         \\
   Mozilla490742                & \Yes                        & \Yes                                             \\
   Mozilla35294                 & \Yes                          & \Yes                                              \\ 
   Mozilla477564                & \Yes                          & \Yes                                            \\
   \midrule 
   MySQL27287                   & \Yes                          & \ding{55}                                         \\
   MySQL15811                   & \Yes                          & \Yes                                      \\ 
   \midrule    
   Apache32546                  & \Yes                          & \Yes                                      \\
   Apache37184                  & \Yes                          & \Yes                                        \\
   Apache29742                  & \Yes                          & \Yes                                       \\ 
   Apache34464                  & \Yes                          & \Yes                                        \\
   Apache47223                  & \Yes                          & \Yes                                       \\
   \midrule
   GCC46401                     & \Yes                     & \Yes                                      \\
   GCC1687                      & \Yes                          & \Yes                                     \\
   GCC27733                     & \Yes                          & \Yes                                     \\
   GCC8805                      & \Yes                          & \Yes                                  \\
   GCC21430                     & \Yes                          & \Yes                                     \\
   GCC12322                     & \Yes                         & \ding{55}                                   \\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Coverage Results.}
  \label{tab:cover}
\end{table}

@@

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
Mozilla\#347306 still incurs the largest overhead (0.49\%). 
The diagnosis results remain the same for all but
GCC\#8805 and GCC\#12322, where too few samples are available
to judge redundancy.

@@

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.7. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.75. The trend is similar for resultless
loop checking.

>>>>

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcc}
    \toprule
                            	&  {\bf Reported}             &{\bf Fix }                     \\
   {\bf BugID}                  &  {\bf Root Cause}           &{\bf Suggestion}             \\
   \midrule
   Mozilla347306                & \Yes                        & \Yes                                          \\
   Mozilla416628                & \Yes                        & \Yes                                         \\
   Mozilla490742                & \Yes                        & \Yes                                             \\
   Mozilla35294                 & \Yes                          & \Yes                                              \\ 
   Mozilla477564                & \Yes                          & \Yes                                            \\
   \midrule 
   MySQL27287                   & \Yes                          & \ding{55}                                         \\
   MySQL15811                   & \Yes                          & \Yes                                      \\ 
   \midrule    
   Apache32546                  & \Yes                          & \Yes                                      \\
   Apache37184                  & \Yes                          & \Yes                                        \\
   Apache29742                  & \Yes                          & \Yes                                       \\ 
   Apache34464                  & \Yes                          & \Yes                                        \\
   Apache47223                  & \Yes                          & \Yes                                       \\
   \midrule
   GCC46401                     & \Yes                     & \Yes                                      \\
   GCC1687                      & \Yes                          & \Yes                                     \\
   GCC27733                     & \Yes                          & \Yes                                     \\
   GCC8805                      & \Yes                          & \Yes                                  \\
   GCC21430                     & \Yes                          & \Yes                                     \\
   GCC12322                     & \Yes                         & \ding{55}                                   \\
\bottomrule
   \end{tabular}
  %\nocaptionrule
\vspace{-0.1in}
  \caption{Coverage Results.}
\vspace{-0.1in}
  \label{tab:cover}
\end{table}

@@

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
Mozilla\#347306 still incurs the largest overhead (0.49\%). 
The diagnosis results remain the same for all but
GCC\#12322, where too few samples are available
to judge redundancy.

@@

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless
loop checking.
